### 2023-06-25 bachelorthesis/24-zonalflows.tex
#39: Rearange heat flux threshold to zonal flows

Furthermore, zonal flows are connected with the radially alternating zonal potential, which introduces a velocity shear, i.e., a radial variation of the zonal flow velocity. This causes a shear deformation of turbulent structures which is considered to play a significant role in the suppression of turbulence \cite{Biglari1990, Dimits2000}, especially the ion temperature gradient driven turbulence \cite{Nakata2012, Makwana2014, Maeyama2014, Whelan2018, Whelan2019}. The shearing process tilts and stretches turbulent eddies, caused by the shear flow, until they break into smaller eddies with reduced radial correlation length [Fig. \ref{fig:zonalflow}],  characterizing the shearing as a decorrelation process. Turbulence will then be reduced because of this process. \cite{Biglari1990,Diamond2005,Burnell1997} The nonlinear generation mechanism causes a shift, also known as Dimits shift \cite{Dimits2000}, of the critical temperature gradient $R/L_{T,\mathrm{c}}$ which leads to a development of ITG-driven turbulence at higher $\rlt$ compared to the linear threshold. \bigskip

@@

As mentioned before the turbulent transport occurs through avalanches which also mediate the turbulence of the ITG-driven turbulence in the adabatic electron approximation. Avalanches are initiated when the $\exb$ sharing rate has a zero crossing with a steep flank and propagates outwards with negative shearing and inwards with positive shearing. \cite{Idomura2009,McMillan2009} The fully developed staircase results in almost completely quenched turbulence. Its development results in a discontinuous step in the dependency of turbulent fluxes on the temperature gradient also known as \textit{finite heat flux threshold}. \cite{Peeters2016,Weikl2017}

>>>>

Furthermore, zonal flows are connected with the radially alternating zonal potential, which introduces a velocity shear, i.e., a radial variation of the zonal flow velocity. This causes a shear deformation of turbulent structures which is considered to play a significant role in the suppression of turbulence \cite{Biglari1990, Dimits2000}, especially the ion temperature gradient driven turbulence \cite{Nakata2012, Makwana2014, Maeyama2014, Whelan2018, Whelan2019}. The shearing process tilts and stretches turbulent eddies, caused by the shear flow, until they break into smaller eddies with reduced radial correlation length [Fig. \ref{fig:zonalflow}],  characterizing the shearing as a decorrelation process. Turbulence will then be reduced because of this process. \cite{Biglari1990,Diamond2005,Burnell1997} The nonlinear generation mechanism causes a shift, also known as Dimits shift \cite{Dimits2000}, of the critical temperature gradient $R/L_{T,\mathrm{c}}$ which leads to a development of ITG-driven turbulence at higher $\rlt$ compared to the linear threshold. This results in a discontinuous step in the dependency of turbulent fluxes on the temperature gradient also known as \textit{finite heat flux threshold}. \cite{Peeters2016,Weikl2017}\bigskip

@@

As mentioned before the turbulent transport occurs through avalanches which also mediate the turbulence of the ITG-driven turbulence in the adabatic electron approximation. Avalanches are initiated when the $\exb$ sharing rate has a zero crossing with a steep flank and propagates outwards with negative shearing and inwards with positive shearing. \cite{Idomura2009,McMillan2009} The fully developed staircase results in almost completely quenched turbulence.
